% !TeX root = ../Template.tex
% [附录]
\appendix
\newpage
下列内容可以作为附录：
\chapter{外文文献}
\section{外文资料}
%外文题目

\chapter*{Alex Trebek admits he was 'writhing in pain' between 'Jeopardy' tapings amid pancreatic cancer battle}

In his first in-home interview since going public with his battle with pancreatic cancer, Alex Trebek discussed the painful struggles he faced – sometimes during a 15-minute break in between Jeopardy tapings – after learning of his diagnosis.

\subsection{{Nothing}}
In an interview with CBS Sunday Morning, Trebek, 78, said that he had been diagnosed with stage four pancreatic cancer while Jeopardy was still in production when his doctors discovered a "small fist" sized lump inside his abdomen.

Still, Trebek, who has filmed nearly 8,000 episodes, was adamant that the show went on, despite sometimes barely making it to his dressing room to "[writhe] in pain."

“This got really bad. I was on the floor writhing in pain. It went from a three to an 11. And I just couldn’t believe. I didn’t know what was happening,” Trebek says. “And it happened three or four times a day while we were taping. So that was a little – little rough on me.”

Trebek told CBS that he would take the 15-minute breaks in between filming episodes of the show, which films a week's worth of episodes in one day, to "get myself together," adding that his spasms lasted about ten to 15 minutes.


%外文题目
\chapter*{亚历克斯特雷贝克承认他在胰腺癌战争中的'危险'录音带中“痛苦地扭动”}

\section{外文翻译}
亚历克斯·特雷贝克（Alex Trebek）在与胰腺癌作斗争上市后首次接受家庭采访时，在得知他的诊断后，讨论了他所面临的痛苦挣扎 - 有时是在危险品拍摄之间的15分钟休息时间。

\subsection{测试小节标题}
在接受哥伦比亚广播公司星期天早晨采访时，78岁的特雷贝克说他被诊断出患有四期胰腺癌，而当他的医生在他的腹部发现一个“小拳头”大小的肿块时，Jeopardy仍在生产。

尽管如此，已经拍摄了近8,000集的特雷贝克仍然坚持认为节目还在继续，尽管有时几乎没有到达他的更衣室“痛苦地”[剧中]。

“这真的很糟糕。我在地板上痛苦地扭动着。它从三个变为十一个。我简直无法相信。我不知道发生了什么，“特雷贝克说。 “当我们录音时，它每天发生三到四次。这对我来说有点粗糙。“

特雷贝克告诉哥伦比亚广播公司，他将在节目的拍摄情节之间进行15分钟的休息，这部电影在一天内播放了一周的剧集，以“让自己在一起”，并补充说他的痉挛持续了大约10到15分钟。


\par * 嗯，自由发挥吧 * \par